paper_pdf

### 2020-03-21 paper_pdf.Rmd
Update paths

prepared_data <- read_csv("../data/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))
food = read.csv("~/data/q1_and_q2.csv")
census <- read_csv("../data/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]

>>>>

prepared_data <- read_csv("~/data/prepared_data.csv", 
    col_types = cols(CHILDPOVRATE15 = col_number(), 
        CONVSPTH09 = col_number(), FFRPTH09 = col_number(), 
        FSRPTH09 = col_number(), GROCPTH09 = col_number(), 
        LACCESS_CHILD10 = col_number(), LACCESS_POP10 = col_number(), 
        METRO13 = col_number(), MILK_PRICE10 = col_number(), 
        PCT_18YOUNGER10 = col_number(), PCT_FREE_LUNCH09 = col_number(), 
        PC_SNAPBEN10 = col_number(), PC_WIC_REDEMP08 = col_number(), 
        PERCHLDPOV10 = col_number(), PERPOV10 = col_number(), 
        RECFACPTH09 = col_number(), SPECSPTH09 = col_number(), 
        SUPERCPTH09 = col_number(), VEG_ACRESPTH07 = col_number()))
food = read.csv("~/data/q1_and_q2.csv")
census <- read_csv("~/data/census.csv")
data <- sqldf::sqldf("SELECT * FROM prepared_data 
              JOIN census
              USING(FIPS)")
data <- data[-c(23,24)]
